%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage[ngerman]{babel}
%\usepackage[applemac]{inputenc}                   % replace by the encoding you are using

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

% VORNAME
\firstname{Verena}
% NACHNAME
\familyname{Pflieger}
%TITEL (optional, ggf. einfach die Zeile löschen!)
\title{Statistician / Data Scientist}    
%ADRESSE  (optional, ggf. einfach die Zeile löschen!)
\address{Andreasberger Str. 8}{12347 Berlin, Germany}
%HANDYNUMMER  (optional, ggf. einfach die Zeile löschen!)
\mobile{+49 176 / 97617237} 
%FESTNETZNUMMER  (optional, ggf. einfach die Zeile löschen!)
\phone{+49 30/61204640}
%EMAIL-ADRESSE  (optional, ggf. einfach die Zeile löschen!)
\email{verenapflieger@gmx.de} 

%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage
%
%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title
%
%\lipsum[1-2] % Dummy text
%\lipsum[4] % Dummy text
%
%\makeletterclosing % Print letter signature
%
%\newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{About me}
\cvline{born on}{August 6th, 1986 in M\"ullheim}
\cvline{profession}{Statistician / Data Scientist}


\section{Education}

\cventry{2010 -- 2013}{Master of Science in Statistics}{FU, HU, TU and Charit\'e}{Berlin}{\textit{Grade: 1,8}}{}  % Arguments not required can be left empty
\cventry{2006 -- 2009}{Bachelor of Arts in Politics and Public Administration}{University of Konstanz}{}{\textit{Grade: 1,8}}{Specialized in Statistics}
\cventry{1997 -- 2006}{General qualification for university entrance}{Markgr\"afler Gymnasium M\"ullheim}{}{\textit{Note: 1,0}}{}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\vspace{1cm}

\section{Experience}

\subsection{Vocational}

\cventry{2016 -- now}{Internal data protection officer}{}{INWT Statistics GmbH, Berlin}{}{Implementation, compliance, and reviewing of the data protection and security both according to BDSG and EU-GDPR.}
\cventry{2014 -- now}{Statistician / Data Scientist}{}{INWT Statistics GmbH, Berlin}{}{Working on projects with data preparation, management, and analysis, consultancy about statistical matters, survey design and questionnaire development, management of training program with personnel responsibility, trainings, data protection officer.}
\cventry{2011 -- 2015 }{Research assistant and student assistant}{}{fu:stat, statistical consulting unit of the Freie Universit\"at, Berlin}{}{Statistical consultancy, management of training program, trainings.}
\cventry{2010 -- 2011}{Student assistant}{}{German Socio Economic Panel (SOEP) of the German Institute for Economic Research (DIW Berlin), Berlin}{}{Handling and analysis of panel data using STATA.}

\clearpage

\subsection{Selected projects}

%\cventry{2017}{Presseaktion}{}{INWT Statistics GmbH, Berlin}{}{Koordination und Leitung der Presseaktion "Wer gewinnt die Bundestagswahl 2017?".}
\cventry{2015 -- now}{Project management}{}{INWT Statistics GmbH, Berlin}{}{Project management (3 team members) for the conceptualisation, implementation, and analysis of a survey within the scope of a longtime customer project.}
\cventry{2015 -- now}{Project}{}{INWT Statistics GmbH, Berlin}{}{Automated reporting in both, PDF and HTML.}
\cventry{2016 -- now}{Data protection according to EU-GDPR}{}{INWT Statistics GmbH, Berlin}{}{Change Management for the implementation of the requirements imposed by the EU-GDPR.}
\cventry{2011}{Scientific report for the BMAS}{}{fu:stat, statistical consulting unit of the Freie Universit\"at, Berlin}{}{Demand analysis about the "Ermittlung der zahlenm\"a\ss igen Gr\"o\ss enordnung von potenziellen Zielgruppen f\"ur eine netzbasierte Weiterbildung zur Altersvorsorge" for the BMAS - Federal Ministry for Labor and Social Affairs.}


\subsection{Teaching}
\cventry{2017 -- now}{DataCamp Online Course (engl.) / concept and implementation}{}{INWT Statistics}{}{Marketing Analytics in R: Statistical Modeling. Customer lifetime modelling with linear regression, churn prevention using logistic regression, modelling time until churn using survival analysis, and dimension reduction with principal component analysis in extensive CRM data.}

\cventry{2017 -- now}{In-house training / concept, coordination, and implementation}{}{INWT Statistics}{}{Basic and advanced level R. Exploratory analysis, inferential statistics, regression analysis, and logistic regression, data handling, recoding of variables, working with weighted data frames, and summary statistics automated by use of functions.}
\cventry{2013 -- 2015}{Workshops / coordination and implementation}{}{fu:stat, statistical consulting unit of the Freie Universit\"at}{}{Basic and advanced methods with R. An introduction to the R programming language, logistic regression, factor analysis, cluster analysis and discriminant analysis using R.}

\cventry{2012 - 2015}{Workshops / coordination and implementation}{}{fu:stat, statistical consulting unit of the Freie Universit\"at}{}{Advanced methods with SPSS. Logistic regression, factor analysis, cluster analysis and discriminant analysis using SPSS.}
\cventry{2012}{Workshop / concept, coordination and implementation}{}{fu:stat, statistical consulting unit of the Freie Universit\"at}{}{Do not trust any statistics! A guide to quantitative research.}

\clearpage


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

%\section{Awards}

%\cvitem{2011}{School of Business Postgraduate Scholarship}
%\cvitem{2010}{Top Achiever Award -- Commerce}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Technical Skills}
\cvitemwithcomment{}{R, STATA, SAS, SPSS, Visual Basic in Excel}{Statistic software, Programming languages}
\cvitemwithcomment{}{Git, Github}{Version-control and development-platform}
\cvitemwithcomment{}{Contao}{Content Management System}
\cvitemwithcomment{}{RMarkdown, LaTex, BibDesk}{Reporting and typesetting}
\cvitemwithcomment{}{Microsoft Office}{Office suite}




%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{Communication Skills}

%\cvitem{2010}{Oral Presentation at the California Business Conference}
%\cvitem{2009}{Poster at the Annual Business Conference in Oregon}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------
\vspace{1cm}

\section{Languages}

\cvitemwithcomment{}{German}{Mother tongue}{}
\cvitemwithcomment{}{English}{Business fluent in spoken and written}
\cvitemwithcomment{}{French}{Conversational in spoken and written}



%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Community service}

\cvitemwithcomment{}{DFC Kreuzberg -- Soccer club for the empowerment of women's soccer}{}
\cvitemwithcomment{}{Invited talks about Data Science at the Datenschule e.V. and the RLadies meetup Berlin}{}

%----------------------------------------------------------------------------------------
%	References
%----------------------------------------------------------------------------------------

\section{References}

\cventry{}{Dr. Claudia Baldermann}{}{former head of fu:stat}{}{claudia.baldermann@fu-berlin.de}
\cventry{}{Dr. Amit Ghosh}{}{managing director of INWT Statistics}{}{amit.ghosh@inwt-statistics.de}



%----------------------------------------------------------------------------------------

\vspace{1cm}

Berlin, \today\\ % Aktuelles Datum und Stadt
\end{document}